Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-12 emsoft-2019/experiments.tex
experimental section, making tables use space properly
info about different used toolboxes is added

% We use Matlab's MPT toolbox~\cite{matlabMPT} to compute the
% explicit MPC, while underlying computations rely on YALMIP(\cite{matlabYALMIP}).
%We evaluate our algorithm with different choices of $\varepsilon_Q$ and $\Delta$.
For the inverted pendulum Matlab's MPT toolbox~\cite{matlabMPT} computes a controller
consisting of $14$ regions with $58$ 2D hyperplanes in total for all choices of $\varepsilon_Q$ and $\Delta$. 
For the aircraft model, Matlab computes a robust EMPC with
$27$ regions and $217$ 4D hyperplanes for most values of $\varepsilon_Q$ and $\Delta$. 
The only exception is when $\Delta=0.30$
and $\varepsilon_Q=0.001$ for which we get $26$ regions having $208$ hyperplanes.
In general, we expect that increasing $\Delta$ results in shrinking of feasible
set size.

@@

%The second difference consists in the last two lines in Table\ref{tab:ipd}.
For the aircraft example, when $\varepsilon_Q=0.0030$, the error due to selecting the wrong region (\maxUij) 
exceeds the given value of $\Delta=0.1$ and our algorithm
needs to design a new controller (corresponding to the \texttt{else} branch in~\autoref{lst:alg}). 
The loop converges after 5 iterations (\texttt{then}
branch in our algorithm) with $\Delta=0.112$. In each iteration, the value
for $\Delta$ is increased by $\varepsilon_{SAFE} = 10^{-3}$.
Thus, the algorithm reduces memory demand
at the expense of slightly more disturbance for the controller. When
$\varepsilon_Q=0.0050$ the analysis converges after 4 iterations.
\eva{Does this mean that for the other settings, the loop in~\autoref{fig:overview}
is executed only once?}

@@

For this example, $\Delta$ and $\varepsilon_Q$ are fixed to $0.1$ and $0.001$,
respectively. By changing the time horizon $N$, we evaluate the scalability
of our approach for controllers with very large number of regions, as 
increasing $N$ generally results in a higher number of regions for the output controller. To
compute the explicit model predictive controllers for different time horizons,
we use Matlab's MPC toolbox. \todo{is this the same as before? If so, add a 'again'}

>>>>

% We use Matlab's MPT toolbox~\cite{matlabMPT} to compute the
% explicit MPC, while underlying computations rely on YALMIP(\cite{matlabYALMIP}).
%We evaluate our algorithm with different choices of $\varepsilon_Q$ and $\Delta$.
We use Matlab's MPT toolbox~\cite{matlabMPT} to compute the explicit MPC, while underlying computations rely on YALMIP(\cite{matlabYALMIP}). For the inverted pendulum MPT toolbox~\cite{matlabMPT} computes a controller
consisting of $14$ regions with $58$ 2D hyperplanes in total for all choices of $\varepsilon_Q$ and $\Delta$. 
For the aircraft model, Matlab computes a robust EMPC with
$27$ regions and $217$ 4D hyperplanes for most values of $\varepsilon_Q$ and $\Delta$. 
The only exception is when $\Delta=0.30$
and $\varepsilon_Q=0.001$ for which we get $26$ regions having $208$ hyperplanes.
In general, we expect that increasing $\Delta$ results in shrinking of feasible
set size.

@@

%The second difference consists in the last two lines in Table\ref{tab:ipd}.
For the aircraft example, when $\varepsilon_Q=0.0030$, the error due to selecting the wrong region (\maxUij) 
exceeds the given value of $\Delta=0.1$ and our algorithm
needs to design a new controller (corresponding to the \texttt{else} branch in~\autoref{lst:alg}). 
The loop converges after 5 iterations (\texttt{then}
branch in our algorithm) with $\Delta=0.112$. In each iteration, the value
for $\Delta$ is increased by $\varepsilon_{SAFE} = 10^{-3}$.
Thus, the algorithm reduces memory demand
at the expense of slightly more disturbance for the controller. When
$\varepsilon_Q=0.0050$ the analysis converges after 4 iterations.
For the other values of $\Delta$ and $\varepsilon$ and for the pendulum example,
the loop in~\autoref{lst:alg} is executed only once.

@@

For this example, $\Delta$ and $\varepsilon_Q$ are fixed to $0.1$ and $0.001$,
respectively. By changing the time horizon $N$, we evaluate the scalability
of our approach for controllers with very large number of regions, as 
increasing $N$ generally results in a higher number of regions for the output controller. To
compute the explicit model predictive controllers for different time horizons,
we use Matlab's MPC toolbox. %\todo{is this the same as before? If so, add a 'again'}
